A Bayesian approach to burial networks to infer social changes in northeastern Taiwan during the European colonization period

### 2021-01-24 analysis/paper/paper.Rmd
correct variable name and knit

# Introduction

@@

## A Case Study from Northeastern Taiwan

@@

# Exponential random graph models in a Baysesian framework

@@

# Materials

@@

# Methods

@@

## Hypothesis and construction of networks

@@

## Model specification in a Bayesian framework

@@

# Reproducibility and open source materials

@@

# Results

@@

# Discussion

@@

# Conclusion

@@

# Acknowledgments

@@

# References 
<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->
<div id="refs"></div>

>>>>

# Introduction {-}

@@

## A Case Study from Northeastern Taiwan  {-}

@@

# Exponential random graph models in a Baysesian framework  {-}

@@

# Materials  {-}

@@

# Methods {-}

@@

## Hypothesis and construction of networks {-}

@@

## Model specification in a Bayesian framework {-}

@@

# Reproducibility and open source materials {-}

@@

# Results {-}

@@

# Discussion {-}

@@

# Conclusion {-}

@@

# Acknowledgments {-}

@@

# References {-} 
<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->
<div id="refs"></div>
